### 2020-11-09 05_Thesis/THESIS_LaTeX/main.tex
thesis match the template

% Your supervisor's name, this is used in the title page, print it elsewhere with \supname and \cosupname
\supervisor{Dr. Héctor Alán \textsc{Aguirre} Soto}
\cosupervisor{Dra. Dora Iliana \textsc{Medina} Medina}

@@

% Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\author{Antonio Osamu \textsc{Katagiri} Tanaka}

@@

% Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\keywords{nanotechnology, carbon, nano-wires, electrospinning, NFES}

@@

@@

\begin{center}
\includegraphics[width=0.15\textwidth]{./Figures/uniLogo.png}
\end{center}

\vspace{0.5cm}
\textsc{\Large Masters Thesis Proposal}\\[0.5cm]      % Thesis type

@@

\begin{minipage}[t]{0.4\textwidth}
\begin{flushleft} \large
\emph{Author:}\\

% Author name - remove the \href bracket to remove the link
\href{https://linkedin.com/in/osamu-katagiri-84b2b940/}{\authorname}
%\authorname
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\begin{flushright} \large
\emph{Principal Advisor:} \\
% Supervisor name - remove the \href bracket to remove the link
%\href{http://www.doramedina.com}{\supname}
\supname

\emph{Co-advisor and\\Director of Program:} \\
% Supervisor name - remove the \href bracket to remove the link
\href{https://www.medinadora.com/}{\cosupname}
%\cosupname
\end{flushright}
\end{minipage}\\[0.5cm]

@@

\large \textit{A thesis proposal submitted in fulfillment of the requirements\\ for the degree of
% University requirement text
\degreename}\\[0.25cm]
\textit{in}\\[0.25cm]
% Research group name and department name
\groupname\\\deptname\\[1cm]

@@

% Address and Date
{\addressname \text{, } \large \today}\\[4cm]
% University/department logo - uncomment to place it
%\includegraphics{./Figures/uniLogo.png}

@@

\begin{committee}
\addchaptertocentry{\supervisingcommittee} % Add the the supervising committee to the table of contents
The committee members, hereby, recommend that the proposal by \authorname \text{ }to be accepted to develop the thesis project as a partial requirement for the degree of \degreename.

@@

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
\supname\\
Tecnológico de Monterrey\\
\emph{Principal Advisor}

@@

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
Dr. Marc \textsc{Madou}\\
Tecnológico de Monterrey\\
\emph{Committee Member}

@@

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
Dr. Sergio Omar \textsc{Martínez} Chapa\\
Tecnológico de Monterrey\\
\emph{Committee Member}

@@

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
\cosupname \\
\emph{Director of Program in Nanotechnology}\\
School of Engineering and Sciences\\
%\href{http://www.doramedina.com}{\supname}

\bigskip
{\addressname \text{, } \large \today}\\[0cm]

@@

\begin{declaration}
\addchaptertocentry{\authorshipname} % Add the declaration to the table of contents
\noindent I, \authorname, declare that this thesis titled, \enquote{\ttitle} and the work presented in it are my own. I confirm that:

\begin{itemize} 
\item This work was done wholly or mainly while in candidature for a research degree at this University.
\item Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
\item Where I have consulted the published work of others, this is always clearly attributed.
\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
\item I have acknowledged all main sources of help.
\item Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.\\
\end{itemize}

\noindent Signed:\\
\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature

\noindent Date:\\
\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
\end{declaration}

@@

%----------------------------------------------------------------------------------------
%	QUOTATION PAGE
%----------------------------------------------------------------------------------------

\vspace*{0.2\textheight}

\begin{center}
\includegraphics[width=0.60\textwidth]{./Figures/quote.png}

\noindent\enquote{\itshape No great discovery was ever made without a bold guess.}\bigbreak
\end{center}

\begin{flushright}
\textbf{Newton, Sir Isaac} \linebreak
In W.I.B. Beveridge \linebreak
\emph{The Art of Scientific Investigation} \linebreak
Scientist (p. 145)
\end{flushright}

@@

\begin{acknowledgements}
\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
There are a number of people without whom this thesis might not have been written,
and to whom I am greatly indebted.\\

@@

I offer my gratitude and appreciation to my supervisors, \supname and \cosupname, for the deft ways in which you fondly challenged and supported me through out the whole of this work - knowing when to push and when to let up. I offer special thanks to those who supported me in the mechanics of producing this thesis. \supname, for reading and rereading drafts, editing and proofing, typing and helping me get ‘unstuck’ with this thesis on many occasions. And Braulio and Arnoldo for ‘rescuing’ me at those times when I was almost defeated by the laboratory equipment.

@@

@@

\listoffigures % Prints the list of figures

\listoftables % Prints the list of tables

@@

\printbibliography[title={References}]

@@

>>>>

% Your supervisor's name, this is used in the title page, print it elsewhere with \supname and \cosupname
\supervisor{Dr. Héctor Alán Aguirre Soto}
\cosupervisor{Dra. Dora Iliana Medina Medina}

@@

% Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\author{Antonio Osamu Katagiri Tanaka}

@@

% Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\keywords{nanotechnology, carbon, nano-wires, Near-Field Electrospinning, NFES}

@@

\examDateAndAddress{\addressname \text{, } \large December 02, 2020}

@@

% Research group name and department name
\campusname\\\deptname\\[1cm]

\begin{center}
\includegraphics[width=0.20\textwidth]{./Figures/uniLogo.png}
\end{center}

\vspace{0.5cm}

@@

\emph{A thesis presented by:}\\

% Author name - remove the \href bracket to remove the link
\href{https://linkedin.com/in/osamu-katagiri-84b2b940/}{\authorname}
%\authorname
\\[0.5cm]

@@

% University requirement text
\large \textit{Submitted to the\\
\deptname\\
in partial fulfillment of the requirements for the degree of}\\[0.25cm]
\textit{Master of Science}\\[0.25cm]
\textit{in}\\[0.25cm]
\textit{Nanotechnology}

@@

% Address and Date
\examDate\\[4cm]
% University/department logo - uncomment to place it
%\includegraphics{./Figures/uniLogo.png}

@@

\begin{committee}
%\addchaptertocentry{\supervisingcommittee} % Add the the supervising committee to the table of contents
The committee members, hereby, certify that have read the dissertation presented by \authorname \text{ } and that it is fully adequate in scope and quality as a partial requirement for the degree of \degreename.

@@

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
\supname\\
Tecnológico de Monterrey\\
\deptname\\
\emph{Principal Advisor}

@@

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
Dr. Marc Madou\\
University of California\\
\emph{Committee Member}

@@

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
%\href{http://www.alanaguirre.com}{\supname}
Dr. Sergio Omar Martínez Chapa\\
Tecnológico de Monterrey\\
\emph{Committee Member}

@@

\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
Dr. Martín Rogelio Bustamante Bello \\
\emph{Associate Dean of Graduate Students}\\
\deptname\\
%\href{http://www.doramedina.com}{\supname}

\bigskip
\examDate\\[0cm]

@@

\begin{declaration}
%\addchaptertocentry{\authorshipname} % Add the declaration to the table of contents
\noindent I, \authorname, declare that this thesis titled, \enquote{\ttitle} and the work presented in it are my own. I confirm that:

\begin{itemize} 
\item This work was done wholly or mainly while in candidature for a research degree at this University.
\item	Where any part of this dissertation has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
\item	Where I have consulted the published work of others, this is always clearly attributed.
\item	Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this dissertation is entirely my own work.
\item	I have acknowledged all main sources of help.
\item	Where the dissertation is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.
\\
\end{itemize}

\begin{flushright}
\noindent \rule[0.0em]{15em}{0.5pt}\\ % This prints a line for the signature
\authorname\\
\examDate
\end{flushright}

\begin{center}
@2020 by \authorname\\
All rights reserved
\end{center}

\end{declaration}

@@

%%----------------------------------------------------------------------------------------
%%	QUOTATION PAGE
%%----------------------------------------------------------------------------------------
%
%\vspace*{0.2\textheight}
%
%\begin{center}
%\includegraphics[width=0.60\textwidth]{./Figures/quote.png}
%
%\noindent\enquote{\itshape No great discovery was ever made without a bold guess.}\bigbreak
%\end{center}
%
%\begin{flushright}
%\textbf{Newton, Sir Isaac} \linebreak
%In W.I.B. Beveridge \linebreak
%\emph{The Art of Scientific Investigation} \linebreak
%Scientist (p. 145)
%\end{flushright}

%----------------------------------------------------------------------------------------
%	DEDICATION
%----------------------------------------------------------------------------------------

\begin{dedication}
%\addchaptertocentry{\dedicationname} % Add the acknowledgements to the table of contents
Thanks for all your unconditional confidence, support, patience, and encouragement. You were my main motivation for pushing through this work.

\end{dedication}

@@

\begin{acknowledgements}
%\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
There are a number of people without whom this thesis might not have been written,
and to whom I am greatly indebted.\\

@@

I offer my gratitude and appreciation to my supervisors, \supname \textit{ } and \cosupname, for the deft ways in which you fondly challenged and supported me through out the whole of this work - knowing when to push and when to let up. I offer special thanks to those who supported me in the mechanics of producing this thesis. \supname, for reading and rereading drafts, editing and proofing, typing and helping me get ‘unstuck’ with this thesis on many occasions. And Braulio and Arnoldo for ‘rescuing’ me at those times when I was almost defeated by the laboratory equipment.

@@

\listoffigures % Prints the list of figures
\addchaptertocentry{\listfigurename} % Add to the table of contents

\listoftables % Prints the list of tables
\addchaptertocentry{\listtablename} % Add to the table of contents

@@

@@

\addcontentsline{toc}{chapter}{Bibliography}
\printbibliography[title={Bibliography}]

@@

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

\newpage 
\addcontentsline{toc}{chapter}{Curriculum Vitae}
\includepdf[page=-,fitpaper=false,landscape=false]{./pdf/CV/CV}
